---
title: "Final Project - En-Chi Kuo"
author: "En-Chi Kuo"
date: "4/11/2022"
output: html_document
---
*International Soccer Team Performance*

Import the data
```{r}
result <- read.csv("~/Downloads/results.csv", header=T)
head(result)
```
Specific countries  to focus on
```{r}
library(dplyr)
England <- filter(result, country == "England" )
France <- filter(result, country == "France")
Italy <- filter(result, country == "Italy")
Malaysia <- filter(result, country == "Malaysia")
Sweden <- filter(result, country == "Sweden" )
Spain <- filter(result, country == "Spain")
US <- filter(result, country == "United States")
new <- rbind(England, France, Italy, Malaysia, Spain, Sweden, US)
```


```{r}
summary(new)
```

Extracting the dates and year of the variable date
```{r}
dates <- as.POSIXct(new$date, format = "%Y-%m-%d")
year<-format(dates,format="%Y")
```

Convert Neutral from ture and false to 0 and 1
```{r}
Neutral <- as.integer(new$neutral)
```

Top 5 games held in the data
```{r}
games_play <- new %>% count(tournament)
Top5 <- games_play %>% top_n(5,n)
head(Top5)
```


```{r}
hist(new$home_score) 
```
```{r}
hist(new$away_score)
```
```{r}
hist(Neutral)
```
Total home score per year by country
```{r}
library(ggplot2)
ggplot(new, aes(x = year, y = home_score, group = country, colour = country)) + 
  geom_line() +
  facet_wrap(~country, scales = 'free_x')
```

Neutral based on home_score by country
```{r}
ggplot(new, aes(x = country, y = home_score, group = neutral, colour = neutral)) + 
  geom_line() +
  facet_wrap(~country, scales = 'free_x')
```

Regression Analysis
```{r}
plot(home_score~away_score, data = new)
```
```{r}
plot(year~Neutral)
```
```{r}
score <- lm(home_score~away_score, data = new)
summary(score)
```


Time Series Analysis: Home Team (England)
```{r}
library(lubridate)
TEngland <- ts(cbind(England$home_score), start = c(2010,1),end=c(2022,3),frequency = 12)
 
# plotting the graph
plot(TEngland, xlab ="Home Team Score Data", 
    main ="International Soccer Game: Home Team Performance (England)",
    col.main ="navy")
summary(TEngland)
```
Time Series Forecasting Analysis: Home Team (England)
```{r}
library(forecast)
myforecast1 <- snaive(TEngland, h=12)
autoplot(myforecast1)
```
```{r}
summary(myforecast1)
```

Time Series Analysis: Home Team (France)
```{r}
TFrance <- ts(cbind(France$home_score), start = c(2010,1),end=c(2022,3),frequency = 12)
 
# plotting the graph
plot(TFrance, xlab ="Awat Team Score Data", 
    main ="International Soccer Game: Away Team Performance",
    col.main ="navy")
summary(TFrance)
```
Time Series Forecasting Analysis: Home Team (France)
```{r}
myforecast2 <- snaive(TFrance, h=12)
autoplot(myforecast2)
```
```{r}
summary(myforecast2)
```


Time Series Analysis: Home Team (Malaysia)
```{r}
TMalaysia <- ts(cbind(Malaysia$home_score), start = c(2010,1),end=c(2022,3),frequency = 12)
 
# plotting the graph
plot(TMalaysia, xlab ="Awat Team Score Data", 
    main ="International Soccer Game: Away Team Performance",
    col.main ="navy")
summary(TMalaysia)
```
Time Series Forecasting Analysis: Home Team (France)
```{r}
myforecast3 <- snaive(TMalaysia, h=12)
autoplot(myforecast3)
```
```{r}
summary(myforecast3)
```

Time Series Analysis: Home Team (Italy)
```{r}
TItaly <- ts(cbind(Italy$home_score), start = c(2010,1),end=c(2022,3),frequency = 12)
 
# plotting the graph
plot(TItaly, xlab ="Awat Team Score Data", 
    main ="International Soccer Game: Away Team Performance",
    col.main ="navy")
summary(TItaly)
```

Time Series Forecasting Analysis: Home Team (Italy)
```{r}
myforecast4 <- snaive(TItaly, h=12)
autoplot(myforecast4)
```
```{r}
summary(myforecast4)
```


Time Series Analysis: Home Team (Spain)
```{r}
TSpain <- ts(cbind(Spain$home_score), start = c(2010,1),end=c(2022,3),frequency = 12)
 
# plotting the graph
plot(TSpain, xlab ="Awat Team Score Data", 
    main ="International Soccer Game: Away Team Performance",
    col.main ="navy")
summary(TSpain)
```

Time Series Forecasting Analysis: Home Team (Spain)
```{r}
myforecast5 <- snaive(TSpain, h=12)
autoplot(myforecast5)
```
```{r}
summary(myforecast5)
```

Time Series Analysis: Home Team (Sweden)
```{r}
TSweden <- ts(cbind(Sweden$home_score), start = c(2010,1),end=c(2022,3),frequency = 12)
 
# plotting the graph
plot(TSweden, xlab ="Awat Team Score Data", 
    main ="International Soccer Game: Away Team Performance",
    col.main ="navy")
summary(TSweden)
```

Time Series Forecasting Analysis: Home Team (Sweden)
```{r}
myforecast6 <- snaive(TSweden, h=12)
autoplot(myforecast6)
```
```{r}
summary(myforecast6)
```


Time Series Analysis: Home Team (US)
```{r}
TUS <- ts(cbind(US$home_score), start = c(2010,1),end=c(2022,3),frequency = 12)
 
# plotting the graph
plot(TUS, xlab ="Awat Team Score Data", 
    main ="International Soccer Game: Away Team Performance",
    col.main ="navy")
summary(TUS)
```

Time Series Forecasting Analysis: Home Team (US)
```{r}
myforecast7 <- snaive(TUS, h=12)
autoplot(myforecast7)
```
```{r}
summary(myforecast7)
```



ANOVA
```{r}
model1 <- lm(new$home_score~new$away_score, new)
plot(model1)
coef(model1)
anova(model1)
```


